\section{Course Materials}\label{course-materials}

Course textbook(s) are \emph{Virology: Principles and Applications} by
John Carter and Venetia Saunders (2007). In addition we might refer to
another book, \emph{Fundamentals of Molecular Virology} by Nicholas
Acheson (2011).

Lecture notes are handed in copy center across our department. PDF
versions of lecture slides can be downloaded from
\href{http://yarbis.yildiz.edu.tr/alyilmaz/course/viewCourse/id/6378}{YARBIS
page}.

Lecture notes contain more pics with sparse text, thus you need to
listen the instructor and take notes.

\section{Grading}\label{grading}

Your grade will come from the following sources:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Midterm: 35\%
\item
  Final: 35\%
\item
  Quiz: 15\%
\item
  Assignment: 10\%
\item
  Attendance: 5\%
\end{itemize}

There will be 4 quizes and 3 highest scores will be considered. If you
attend all lectures or miss only one lecture then you'll get 5 points.
For every 1-2 lectures missed you'll lose 1 point.

Final exam will be from lectures discussed after Midterm exam.

Number and content of assignments will be provided later. The
assignments will be related to ``applications of a given virus to
bioengineering problems''.

\section{Communication}\label{communication}

I'm trying to respond emails as quickly as possible. If you don't get a
response within 1-2 days please don't hesitate to send a reminder email.

The changes pertaining to exam date, time and assignment due dates
should be decided in class after discussing with everybody. Please don't
ask for changes individually, otherwise notification of whole class
becomes a hassle.
