\section{Schedule}\label{schedule}

Below is the tentative schedule for the course. Depending on the speed
we go through topics there might be shifts in the schedule.

\subsubsection{February 15.
Introduction}\label{february-15.-introduction}

Introduction to virology and various fields related to virology.
Overview of complexity and diversity of viruses, their genomes an
proteins. Main differences between enveloped and non-enveloped viruses.

\subsubsection{February 22. Methods Used in Virology \& Virus
Structure}\label{february-22.-methods-used-in-virology-virus-structure}

\emph{Chapter 2} and \emph{Chapter 3} in our textbook.

\subsection{Mechanisms}\label{mechanisms}

\subsubsection{February 29. Attachment, Entry, Translation and
Transport}\label{february-29.-attachment-entry-translation-and-transport}

\emph{Chapter 5} and \emph{Chapter 6} in our textbook.

\subsubsection{March 7. Virus Genome Replication \& Assembly and
Exit}\label{march-7.-virus-genome-replication-assembly-and-exit}

\emph{Chapter 7} and \emph{Chapter 8} in our textbook.

\subsubsection{March 7. Classification and Nomenclature of
Viruses}\label{march-7.-classification-and-nomenclature-of-viruses}

\emph{Chapter 10} in our textbook.

\subsection{Individual Virus Families}\label{individual-virus-families}

\subsubsection{March 14. Herpesviruses and Other dsDNA
Viruses}\label{march-14.-herpesviruses-and-other-dsdna-viruses}

\emph{Chapter 11} in our textbook.

\subsubsection{March 21. Parvoviruses and Other ssDNA
Viruses}\label{march-21.-parvoviruses-and-other-ssdna-viruses}

\emph{Chapter 12} in our textbook.

\subsubsection{March 28. Reoviruses and Other dsRNA
Viruses}\label{march-28.-reoviruses-and-other-dsrna-viruses}

\emph{Chapter 13} in our textbook.

\subsubsection{April 4. Picornaviruses and Other Plus-strand RNA
Viruses}\label{april-4.-picornaviruses-and-other-plus-strand-rna-viruses}

\emph{Chapter 14} in our textbook.

\subsubsection{(April 11). Midterm}\label{april-11.-midterm}

\subsubsection{April 18. Rhabdoviruses and Other Minus-strand RNA
Viruses}\label{april-18.-rhabdoviruses-and-other-minus-strand-rna-viruses}

\emph{Chapter 15} in our textbook.

\subsubsection{April 25. Retroviruses}\label{april-25.-retroviruses}

\emph{Chapter 16} in our textbook.

\subsubsection{May 2. Retroviruses (cont'd) \&
HIV}\label{may-2.-retroviruses-contd-hiv}

\emph{Chapter 16} and \emph{Chapter 17} in our textbook.

\subsubsection{May 9. Hepadnaviruses and Other Reverse-transcribing DNA
Viruses}\label{may-9.-hepadnaviruses-and-other-reverse-transcribing-dna-viruses}

\emph{Chapter 18} in our textbook

\subsubsection{May 16. Evolution and Emerging of
Viruses}\label{may-16.-evolution-and-emerging-of-viruses}

\emph{Chapter 20} and \emph{Chapter 21} in our textbook.

\subsubsection{May 23. Resistance of Infectivity and Vaccines (Final
Lecture).}\label{may-23.-resistance-of-infectivity-and-vaccines-final-lecture.}

\emph{Chapter 23} and \emph{Chapter 24} in our textbook.
